---
title: "ADH -- Double the flies"
author: "TS O'Leary"
output:
  rmarkdown::html_document:
    theme: lumen
    toc: true
    toc_float: true
---

```{r setup, include = FALSE}
# Set up chunk defaults
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

# Load packages
require(tidyverse)
require(broom)
require(RColorBrewer)
require(kableExtra)

# Source required functions
source(here::here("ADH/scripts/adh_batch_functions.R"))
```

# Reaction Velocities

```{r}
# Read in data -----------------------------------------------------------------
data_f <- read_bind_tidy_csv(dir = here::here("ADH/data/double_enz_conc/adh-f")) %>%
  filter(time <= 35)
data_s <- read_bind_tidy_csv(dir = here::here("ADH/data/double_enz_conc/adh-s")) %>%
  filter(time <= 35)

```{r}
# Calculate reaction velocities at each [EtOH] and each Temp group -------------
data_velo_f <- calc_velocity(data_f)
data_velo_s <- calc_velocity(data_s)
```

## ADH-fast enzyme
```{r, fig.height = 7, fig.width = 10}
plot_velo(data_f)
data_velo_f %>%
  select(temp_group, conc, velocity, r.squared) %>%
  kable() %>%
  kable_styling("striped") %>%
  scroll_box(width = "100%", height = "500px")
```

## ADH-slow enzyme

```{r, fig.height = 7, fig.width = 10}
plot_velo(data_s)
data_velo_s %>%
  select(temp_group, conc, velocity, r.squared) %>%
  kable() %>%
  kable_styling("striped") %>%
  scroll_box(width = "100%", height = "500px")
```

# Fit Michaelis–Menten curves

```{r}
# Determine the Km and Vmax from the fit of the Michaelis–Menten curves --------
data_Km_Vm_f <- calc_Km_Vm(data_velo_f)
data_Km_Vm_s <- calc_Km_Vm(data_velo_s)
```

## ADH-fast enzyme
```{r}
plot_mm_curve(data_velo_f)
```

## ADH-slow enzyme

```{r}
plot_mm_curve(data_velo_s)
```

# Plot K<sub>m</sub> values

```{r}
# Combine Km tibbles -----------------------------------------------------------
df_km_plot <- bind_rows("fast" = data_Km_Vm_f, 
                        "slow" = data_Km_Vm_s, 
                        .id = "enzyme") %>%
  mutate(enzyme = factor(enzyme, levels = c("fast", "slow"))) %>%
  select(enzyme, temp_group, term, estimate, std.error, r.squared) %>%
  pivot_wider(names_from = term, 
              values_from = c(estimate, std.error))

df_km_plot %>%
  select(enzyme, temp_group, contains("Km"), r.squared) %>%
  mutate(`Km (± SEM)`= 
           paste0(round(estimate_Km, 2), " (± ", 
                  round(std.error_Km, 2), ")")) %>%
  select(enzyme, temp_group, `Km (± SEM)`, r.squared) %>%
  arrange(enzyme, temp_group) %>%
  kable() %>%
  kable_styling("striped") %>%
  scroll_box(width = "100%", height = "100%")

# Plot all Km's on the same chart
plot_km(df_km_plot)
```
